% !TEX program = pdflatex
%
% Detailed publication list for Siu Lun Chau.
% Citation counts and venues sourced from Google Scholar (12 May 2026).
% Full author lists and titles sourced from publications.bib.
% Grouped by publication type; ordered chronologically (newest first)
% within each group, with citation count as a tie-breaker.
%
\documentclass[11pt,a4paper]{article}

% ---------- Packages ----------
\usepackage[margin=2cm,top=2.2cm,bottom=2.2cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{charter}
\linespread{1.05}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[skip=3pt plus 1pt minus 1pt]{parskip}
\usepackage{etoolbox}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}

% ---------- Colours ----------
\definecolor{accent}{HTML}{1F4E79}
\definecolor{award}{HTML}{B22222}
\definecolor{citecol}{HTML}{2E7D32}
\definecolor{mutedgrey}{HTML}{777777}
\hypersetup{colorlinks=true,linkcolor=accent,urlcolor=accent,citecolor=accent}

% ---------- Layout ----------
\setcounter{secnumdepth}{0}
\titleformat{\section}{\Large\bfseries\color{accent}}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{4pt}

% ---------- Helpers ----------
\newcommand{\me}{\textbf{Siu Lun Chau}}
\newcommand{\acro}[1]{\textcolor{accent}{\textbf{#1}}}
\newcommand{\award}[1]{\textcolor{award}{\textbf{#1}}}
\newcommand{\venue}[2]{\textit{#1} (\acro{#2})}
\newcommand{\venueplain}[1]{\textit{#1}}
\newcommand{\pdfb}[1]{\,\href{#1}{\textcolor{accent}{\small[pdf]}}}
\newcommand{\codeb}[1]{\,\href{#1}{\textcolor{accent}{\small[code]}}}
\newcommand{\videob}[1]{\,\href{#1}{\textcolor{accent}{\small[video]}}}

\newlength{\citecolwidth}\setlength{\citecolwidth}{2.4cm}
\newlength{\indexcolwidth}\setlength{\indexcolwidth}{3.2em}
\newcommand{\citebox}[2]{%
  {\color{citecol}\textbf{\large #1}}\\[1pt]
  {\color{mutedgrey}\small #2}%
}
\newcommand{\pubentry}[4]{%
  \noindent
  \makebox[\indexcolwidth][l]{\textbf{[#1]}}%
  \begin{minipage}[t]{\dimexpr\linewidth-\indexcolwidth-\citecolwidth-0.4em\relax}#2\end{minipage}%
  \hspace{0.4em}%
  \begin{minipage}[t]{\citecolwidth}\raggedleft\citebox{#3}{#4}\end{minipage}%
  \par\vspace{6pt}}

% ---------- Footer ----------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\small\color{accent}Siu Lun Chau --- Publications}
\fancyfoot[C]{\small\color{accent}Compiled: May 12, 2026}
\fancyfoot[R]{\small\color{accent}\thepage~/~\pageref*{LastPage}}
\fancypagestyle{plain}{\fancyhf{}\renewcommand{\headrulewidth}{0pt}%
  \fancyfoot[L]{\small\color{accent}Siu Lun Chau --- Publications}%
  \fancyfoot[C]{\small\color{accent}Compiled: May 12, 2026}%
  \fancyfoot[R]{\small\color{accent}\thepage~/~\pageref*{LastPage}}}

\begin{document}

% ---------- Title block ----------
\noindent
{\Huge\bfseries\color{accent} Siu Lun Chau}\\[4pt]
{\large List of Publications}\\[2pt]
\textit{Assistant Professor, College of Computing \& Data Science, Nanyang Technological University}\\
\textit{Principal Investigator, Epistemic Intelligence \& Computation Lab}

\vspace{6pt}

% ---------- Citation Summary ----------
\noindent
\begin{tabularx}{\linewidth}{@{}lcccc@{}}
\toprule
\textbf{Google Scholar (12 May 2026)} & \textbf{Citations} & \textbf{h-index} & \textbf{i10-index} & \textbf{Publications listed} \\
\midrule
All time   & 466 & 13 & 14 & 36 \\
Since 2021 & 465 & 13 & 14 & --- \\
\bottomrule
\end{tabularx}

\vspace{4pt}
\noindent\small Author's name is set in \textbf{bold}. Venue acronyms appear in {\color{accent}\textbf{blue}}. Awards/honours are in {\color{award}\textbf{red}}. The right-hand column shows the {\color{citecol}\textbf{citation count}} (from Google Scholar at the date above) and the publication year. Co-first authorship is marked with $^{*}$. Entries within each section are ordered by year (newest first); within the same year they are ordered by citation count.
\normalsize

% ---------- Venue legend ----------
\section{Venue Acronyms}
\noindent
\begin{tabularx}{\linewidth}{@{}lX@{}}
\acro{NeurIPS}    & Conference on Neural Information Processing Systems \\
\acro{ICML}       & International Conference on Machine Learning \\
\acro{AISTATS}    & International Conference on Artificial Intelligence and Statistics \\
\acro{AAAI}       & AAAI Conference on Artificial Intelligence \\
\acro{UAI}        & Conference on Uncertainty in Artificial Intelligence \\
\acro{ECML-PKDD}  & European Conference on Machine Learning and Principles \& Practice of Knowledge Discovery in Databases \\
\acro{Nat.~Comm.} & Nature Communications \\
\acro{TMLR}       & Transactions on Machine Learning Research \\
\acro{IEEE TSIPN} & IEEE Transactions on Signal and Information Processing over Networks \\
\end{tabularx}

% =====================================================================
\section{Journal Articles}
% =====================================================================

\pubentry{J1}{%
\textbf{Highly Parallel Optimisation of Chemical Reactions through Automation and Machine Intelligence.}\\
Joshua W.\ Sin, \me, Ryan P.\ Burwood, Kurt P\"untener, Raphael Bigler, Philippe Schwaller.\\
\venue{Nature Communications}{Nat.~Comm.}, vol.~16(1), 6464.%
\pdfb{https://chemrxiv.org/engage/chemrxiv/article-details/66f976b5cec5d6c142981e4e}\codeb{https://github.com/schwallergroup/minerva}%
}{32}{2025}

\pubentry{J2}{%
\textbf{Gated Domain Units for Multi-source Domain Generalization.}\\
Simon F\"oll, Alina Dubatovka, Eugen Ernst, \me, Martin Maritsch, Patrik Okanovic, Gudrun Thaeter, Joachim M.\ Buhmann, Felix Wortmann, Krikamol Muandet.\\
\venue{Transactions on Machine Learning Research}{TMLR}.%
\pdfb{https://arxiv.org/pdf/2206.12444.pdf}\codeb{https://github.com/im-ethz/pub-gdu4dg}%
}{7}{2023}

\pubentry{J3}{%
\textbf{Kernel-based Graph Learning from Smooth Signals: A Functional Viewpoint.}\\
Xingyue Pu, \me, Xiaowen Dong, Dino Sejdinovic.\\
\venue{IEEE Transactions on Signal and Information Processing over Networks}{IEEE TSIPN}, vol.~7, pp.~192--207.%
\pdfb{https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=9356326}%
}{30}{2021}

% =====================================================================
\section{Conference \& Workshop Papers (Peer-Reviewed)}
% =====================================================================

% ----- 2026 -----
\pubentry{C1}{%
\textbf{Exact Shapley Attributions in Quadratic-time for fANOVA Gaussian Processes.}\\
Majid Mohammadi, Krikamol Muandet, Ilaria Tiddi, Annette Ten Teije, \me.\\
\venue{Proceedings of the AAAI Conference on Artificial Intelligence}{AAAI 2026}, vol.~40(29), pp.~24414--24421.%
\pdfb{https://arxiv.org/pdf/2508.14499v1}%
}{5}{2026}

\pubentry{C2}{%
\textbf{Explanation Design in Strategic Learning: Sufficient Explanations that Induce Non-harmful Responses.}\\
Kiet QH Vo, \me, Masahiro Kato, Yixin Wang, Krikamol Muandet.\\
\venue{29th International Conference on Artificial Intelligence and Statistics}{AISTATS 2026}.%
\pdfb{https://arxiv.org/pdf/2502.04058}\codeb{https://github.com/muandet-lab/sl-leaf}%
}{3}{2026}

\pubentry{C3}{%
\textbf{Learning Credal Ensembles via Distributionally Robust Optimization.}\\
Kaizheng Wang, Ghifari Adam Faza, Fabio Cuzzolin, \me, David Moens, Hans Hallez.\\
\venue{International Conference on Machine Learning}{ICML 2026} --- \award{Spotlight}.%
\pdfb{https://arxiv.org/pdf/2602.08470}%
}{1}{2026}

\pubentry{C4}{%
\textbf{Off-Policy Evaluation with Strategic Agents via Local Disclosure.}\\
Kiet QH Vo, Abbavaram Gowtham Reddy, Julian Rodemann, \me, Krikamol Muandet.\\
\venue{International Conference on Machine Learning}{ICML 2026}.%
}{--}{2026}

% ----- 2025 -----
\pubentry{C5}{%
\textbf{Credal Two-Sample Tests of Epistemic Uncertainty.}\\
\me, Antonin Schrab, Arthur Gretton, Dino Sejdinovic, Krikamol Muandet.\\
\venue{International Conference on Artificial Intelligence and Statistics}{AISTATS 2025}, PMLR, pp.~127--135.%
\pdfb{https://arxiv.org/pdf/2410.12921}\codeb{https://github.com/muandet-lab/CredalTwoSampleTests}\videob{https://www.youtube.com/watch?v=Rq9qW0GZJeE}%
}{29}{2025}

\pubentry{C6}{%
\textbf{Integral Imprecise Probability Metrics.}\\
\me, Michele Caprio, Krikamol Muandet.\\
\venue{Thirty-ninth Annual Conference on Neural Information Processing Systems}{NeurIPS 2025}.%
\pdfb{https://arxiv.org/pdf/2505.16156}%
}{13}{2025}

\pubentry{C7}{%
\textbf{Truthful Elicitation of Imprecise Forecasts.}\\
Anurag Singh, \me, Krikamol Muandet.\\
\venue{Conference on Uncertainty in Artificial Intelligence}{UAI 2025}, PMLR, pp.~3898--3919 --- \award{Oral}.%
\pdfb{http://arxiv.org/pdf/2503.16395}\codeb{https://github.com/muandet-lab/Imprecise-Scoring-Rule}%
}{8}{2025}

\pubentry{C8}{%
\textbf{Kernel Quantile Embeddings and Associated Probability Metrics.}\\
Masha Naslidnyk, \me, Fran\c cois-Xavier Briol, Krikamol Muandet.\\
\venue{International Conference on Machine Learning}{ICML 2025}, PMLR, pp.~45770--45800.%
\pdfb{https://arxiv.org/pdf/2505.20433}%
}{1}{2025}

% ----- 2024 -----
\pubentry{C9}{%
\textbf{Looping in the Human: Collaborative and Explainable Bayesian Optimization.}\\
Masaki Adachi, Brady Planden, David Howey, Michael A.\ Osborne, Sebastian Orbell, Natalia Ares, Krikamol Muandet, \me.\\
\venue{International Conference on Artificial Intelligence and Statistics}{AISTATS 2024}, PMLR, pp.~505--513.%
\pdfb{https://arxiv.org/pdf/2310.17273.pdf}\codeb{https://anonymous.4open.science/r/CoExBO-4B06/}%
}{40}{2024}

\pubentry{C10}{%
\textbf{Domain Generalisation via Imprecise Learning.}\\
Anurag Singh, \me, Shahine Bouabid, Krikamol Muandet.\\
\venue{41st International Conference on Machine Learning}{ICML 2024}, pp.~45544--45570 --- \award{Spotlight}.%
\pdfb{https://arxiv.org/pdf/2404.04669}\codeb{https://github.com/muandet-lab/dgil}%
}{25}{2024}

\pubentry{C11}{%
\textbf{Causal Strategic Learning with Competitive Selection.}\\
Kiet QH Vo, Muneeb Aadil, \me, Krikamol Muandet.\\
\venue{Proceedings of the AAAI Conference on Artificial Intelligence}{AAAI 2024}, vol.~38(14), pp.~15411--15419 --- \award{Oral}.%
\pdfb{https://arxiv.org/pdf/2308.16262.pdf}\codeb{https://github.com/muandet-lab/causal-strategic-learning-with-selection}%
}{11}{2024}

% ----- 2023 -----
\pubentry{C12}{%
\textbf{Explaining the Uncertain: Stochastic Shapley Values for Gaussian Process Models.}\\
\me, Krikamol Muandet, Dino Sejdinovic.\\
\venue{Advances in Neural Information Processing Systems}{NeurIPS 2023}, vol.~36, pp.~50769--50795 --- \award{Spotlight}.%
\pdfb{https://arxiv.org/pdf/2305.15167.pdf}\codeb{https://github.com/muandet-lab/ExplainingGaussianProcess}\videob{https://slideslive.com/39009992/explaining-the-uncertain-stochastic-shapley-values-for-gaussian-process-models}%
}{41}{2023}

% ----- 2022 -----
\pubentry{C13}{%
\textbf{RKHS-SHAP: Shapley Values for Kernel Methods.}\\
\me, Robert Hu, Javier Gonzalez, Dino Sejdinovic.\\
\venue{Advances in Neural Information Processing Systems}{NeurIPS 2022}, vol.~35, pp.~13050--13063.%
\pdfb{https://proceedings.neurips.cc/paper_files/paper/2022/file/54bb63eaec676b87a2278a22b1bd02a2-Paper-Conference.pdf}\codeb{https://github.com/Chau999/RKHS-SHAP}\videob{https://www.youtube.com/watch?v=olmSYH-daG0}%
}{63}{2022}

\pubentry{C14}{%
\textbf{Spectral Ranking with Covariates.}\\
\me, Mihai Cucuringu, Dino Sejdinovic.\\
\venue{Joint European Conference on Machine Learning and Knowledge Discovery in Databases}{ECML-PKDD 2022}, Springer, pp.~70--86.%
\pdfb{https://arxiv.org/pdf/2005.04035.pdf}\codeb{https://github.com/Chau999/SpectralRankingWithCovariates}%
}{20}{2022}

\pubentry{C15}{%
\textbf{Learning Inconsistent Preferences with Gaussian Processes.}\\
\me, Javier Gonzalez, Dino Sejdinovic.\\
\venue{International Conference on Artificial Intelligence and Statistics}{AISTATS 2022}, PMLR, pp.~2266--2281.%
\pdfb{https://proceedings.mlr.press/v151/lun-chau22a/lun-chau22a.pdf}\videob{https://slideslive.at/38980474/learning-inconsistent-preferences-with-gaussian-processes}%
}{18}{2022}

\pubentry{C16}{%
\textbf{Explaining Preferences with Shapley Values.}\\
Robert Hu$^{*}$, \me$^{*}$, Jaime Ferrando Huertas, Dino Sejdinovic ($^{*}$ co-first authors).\\
\venue{Advances in Neural Information Processing Systems}{NeurIPS 2022}, vol.~35, pp.~27664--27677.%
\pdfb{https://proceedings.neurips.cc/paper_files/paper/2022/file/b1656d20067ca7c84a33785c4083a75e-Paper-Conference.pdf}\codeb{https://github.com/MrHuff/PREF-SHAP}\videob{https://slideslive.com/38992229/explaining-preferences-with-shapley-values}%
}{17}{2022}

\pubentry{C17}{%
\textbf{Giga-scale Kernel Matrix-Vector Multiplication on GPU.}\\
Robert Hu, \me, Dino Sejdinovic, Joan Glaun\`es.\\
\venue{Advances in Neural Information Processing Systems}{NeurIPS 2022}, vol.~35, pp.~9045--9057.%
\pdfb{https://arxiv.org/pdf/2202.01085.pdf}\codeb{https://anonymous.4open.science/r/F3M-7850/readme.md}%
}{4}{2022}

% ----- 2021 -----
\pubentry{C18}{%
\textbf{Deconditional Downscaling with Gaussian Processes.}\\
\me$^{*}$, Shahine Bouabid$^{*}$, Dino Sejdinovic ($^{*}$ co-first authors).\\
\venue{Advances in Neural Information Processing Systems}{NeurIPS 2021}, vol.~34, pp.~17813--17825.%
\pdfb{https://proceedings.neurips.cc/paper/2021/hash/96f2b50b5d3613adf9c27049b3a839b6-Abstract.html}\codeb{https://github.com/shahineb/deconditional-downscaling}\videob{https://slideslive.com/38967430/deconditional-downscaling-with-gaussian-processes}%
}{40}{2021}

\pubentry{C19}{%
\textbf{BayesIMP: Uncertainty Quantification for Causal Data Fusion.}\\
\me$^{*}$, Jean-Francois Ton$^{*}$, Javier Gonz\'alez, Yee Whye Teh, Dino Sejdinovic ($^{*}$ co-first authors).\\
\venue{Advances in Neural Information Processing Systems}{NeurIPS 2021}, vol.~34, pp.~3466--3477.%
\pdfb{https://proceedings.neurips.cc/paper/2021/file/1ca5c750a30312d1919ae6a4d636dcc4-Paper.pdf}\videob{https://slideslive.com/38968202/bayesimp-uncertainty-quantification-for-causal-data-fusion}%
}{36}{2021}

% =====================================================================
\section{Doctoral Thesis}
% =====================================================================

\pubentry{T1}{%
\textbf{Towards Trustworthy Machine Learning with Kernels.}\\
\me.\\
\venueplain{DPhil (PhD) Thesis, University of Oxford}.%
\pdfb{https://ora.ox.ac.uk/objects/uuid:24c81031-e078-4481-a677-e7a51b659bfc}%
}{1}{2023}

% =====================================================================
\section{Preprints (Under Review / arXiv)}
% =====================================================================

% ----- 2026 -----
\pubentry{P1}{%
\textbf{Quantifying Epistemic Predictive Uncertainty in Conformal Prediction.}\\
\me, Soroush H.\ Zargarbashi, Yusuf Sale, Michele Caprio.\\
\venueplain{arXiv preprint arXiv:2602.01667}.%
\pdfb{https://arxiv.org/pdf/2602.01667}\codeb{https://anonymous.4open.science/r/ConformalMMI-1244/README.md}%
}{3}{2026}

\pubentry{P2}{%
\textbf{QuadraSHAP: Stable and Scalable Shapley Values for Product Games via Gauss--Legendre Quadrature.}\\
Majid Mohammadi, Grigory Reznikov, Pavel Sinitcyn, Krikamol Muandet, \me.\\
\venueplain{arXiv preprint arXiv:2605.05870}.%
\pdfb{https://arxiv.org/pdf/2605.05870}%
}{--}{2026}

\pubentry{P3}{%
\textbf{Measuring Differences between Conditional Distributions using Kernel Embeddings.}\\
Peter Moskvichev, \me, Dino Sejdinovic.\\
\venueplain{arXiv preprint arXiv:2605.02260}.%
}{--}{2026}

\pubentry{P4}{%
\textbf{Quantification of Credal Uncertainty: A Distance-Based Approach.}\\
Xabier Gonzalez-Garcia, \me, Julian Rodemann, Michele Caprio, Krikamol Muandet, Humberto Bustince, S\'ebastien Destercke, Eyke H\"ullermeier, Yusuf Sale.\\
\venueplain{arXiv preprint arXiv:2603.27270}.%
\pdfb{https://arxiv.org/abs/2603.27270}%
}{--}{2026}

\pubentry{P5}{%
\textbf{Verbalizing LLM's Higher-order Uncertainty via Imprecise Probabilities.}\\
Anita Yang, Krikamol Muandet, Michele Caprio, \me, Masaki Adachi.\\
\venueplain{arXiv preprint arXiv:2603.10396}.%
\pdfb{https://arxiv.org/pdf/2603.10396}%
}{--}{2026}

\pubentry{P6}{%
\textbf{Incentive Aware AI Regulations: A Credal Characterisation.}\\
Anurag Singh, Julian Rodemann, Rajeev Verma, \me, Krikamol Muandet.\\
\venueplain{arXiv preprint arXiv:2603.05175}.%
\pdfb{https://arxiv.org/pdf/2603.05175}\codeb{https://github.com/muandet-lab/incentive-aware-ai-regulation}%
}{--}{2026}

\pubentry{P7}{%
\textbf{Instrumental and Proximal Causal Inference with Gaussian Processes.}\\
Yuqi Zhang, Krikamol Muandet, Dino Sejdinovic, Edwin Fong, \me.\\
\venueplain{arXiv preprint arXiv:2603.02159}.%
\pdfb{https://arxiv.org/pdf/2603.02159}%
}{--}{2026}

\pubentry{P8}{%
\textbf{Set-based vs Distribution-based Representations of Epistemic Uncertainty: A Comparative Study.}\\
Kaizheng Wang, Yunjia Wang, Fabio Cuzzolin, David Moens, Hans Hallez, \me.\\
\venueplain{arXiv preprint arXiv:2602.22747}.%
\pdfb{https://arxiv.org/pdf/2602.22747}%
}{--}{2026}

\pubentry{P9}{%
\textbf{Robust Predictive Uncertainty and Double Descent in Contaminated Bayesian Random Features.}\\
Michele Caprio, Katerina Papagiannouli, \me, Sayan Mukherjee.\\
\venueplain{arXiv preprint arXiv:2602.19126}.%
\pdfb{https://arxiv.org/pdf/2602.19126}%
}{--}{2026}

% ----- 2025 -----
\pubentry{P10}{%
\textbf{Amortized Linear-time Exact Shapley Value for Product-Kernel Methods.}\\
Majid Mohammadi$^{*}$, \me$^{*}$, Krikamol Muandet ($^{*}$ co-first authors).\\
\venueplain{arXiv preprint arXiv:2505.16516} (also listed on Scholar as ``Computing exact Shapley values in polynomial time for product-kernel methods'').%
\pdfb{https://arxiv.org/pdf/2505.16516}%
}{9}{2025}

\pubentry{P11}{%
\textbf{Bayesian Optimization for Building Social-Influence-Free Consensus.}\\
Masaki Adachi, \me, Wenjie Xu, Anurag Singh, Michael A.\ Osborne, Krikamol Muandet.\\
\venueplain{arXiv preprint arXiv:2502.07166}.%
\pdfb{https://arxiv.org/pdf/2502.07166}%
}{7}{2025}

\pubentry{P12}{%
\textbf{When Do Credal Sets Stabilize? Fixed-Point Theorems for Credal Set Updates.}\\
Michele Caprio, \me, Krikamol Muandet.\\
\venueplain{arXiv preprint arXiv:2510.04769}.%
\pdfb{https://arxiv.org/pdf/2510.04769}%
}{2}{2025}

\vspace{6pt}
\noindent\small\textit{End of publication list. Total entries: 36
(3 journals, 19 conference/workshop papers, 1 thesis, 12 preprints).
Citation counts current as of 12 May 2026. ``--'' denotes a publication not yet cited on Google Scholar.}

\end{document}
